Dynamics of International Giving: How Heuristics Shape Individual Donor Preferences

### 2020-09-30 manuscript/manuscript.Rmd
Use Zenodo DOI for GitHub repo

To measure the effect of structural and organization-level heuristics on individual donor preferences, we use an experiment to vary the different frames donors are exposed to. Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs tailor their fundraising strategies for individuals. Prior to launching the experiment, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at <https://doi.org/10.17605/OSF.IO/DX973>. The online appendix also includes the full text of the survey experiment, as well as details about our sample demographics, balance across experimental conditions, CONSORT diagram, and Bayesian priors. The analysis is fully reproducible using code and data available at <https://github.com/andrewheiss/ngo-crackdowns-philanthropy> and <https://dx.doi.org/10.17605/OSF.IO/FG53W>.

>>>>

To measure the effect of structural and organization-level heuristics on individual donor preferences, we use an experiment to vary the different frames donors are exposed to. Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs tailor their fundraising strategies for individuals. Prior to launching the experiment, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at <https://doi.org/10.17605/OSF.IO/DX973>. The online appendix also includes the full text of the survey experiment, as well as details about our sample demographics, balance across experimental conditions, CONSORT diagram, and Bayesian priors. The analysis is fully reproducible using code and data available at <https://doi.org/10.5281/zenodo.4058986> and <https://dx.doi.org/10.17605/OSF.IO/FG53W>.
